\verse{Some sixteen and two-thousand years
Since the birth of Christ our Lord,
Our noble brigade was likewise betrayed
By a breach of sacred word.
Our Judas was a band of thieves
Entrusted with the care
Of that place, whence we came, called the Pleasance by name,
Though you'll find no more Pleasance there.}

\verse{Though our foes of yore, they had promised before 
That they always would honour our rights.
Trusting all that we heard, we wrote down not a word
Thus began our descent into night.
We join the ranks of those poor souls 
by Satan's tongue misled;
Though not fallen to Hell, nor from Eden expelled
A most perilous path did we tread.}

\verse{So we looked high and low for place we might go
And at length made an end to our search.
As so many before turned away from their doors
We have found our refuge in the Church.
But though we no more roam still we long for a home
For a room of our own do we yearn,
And let you, sir, take note though our enemies gloat,
Even now do we plot our return!}

\verse{We were driven forth in banishment
By the cruel usurper's hand,
But onward we'll go and by action we'll show
We're beholden to nary a man.
It is said all men are born in sin
And you, sir, prove it true,
But our will it is strong
And you'll know before long
We are mightier than (E) you (SA).}

\verse{So if you, sir, think we won't outlast this decree,
Let us think upon this rule:
``Fa dhe\`{o}igh thig cr\`{i}och air an t-saoghail
Ach mairidh ce\`{o}l agus gaol".
A saying of the Scottish Gael,
The truth of which is sure:
``At last the Earth itself will end,
But music and love will endure."}