\verse{When I was a young lad I used to like girls,
I'd fondle their bodies and play with their curls,
But my girlfriend ran off with my ex-best friend Bruce,
And I'll never get treatment like that from a moose.}

\chorus{So it's moose, moose, I like a moose!
I've never had anything quite like a moose.
I've had many lovers, my morals are loose,
But I've never had anything quite like a moose.}

\verse{So when I'm in the need for a really good lay,
I go to my bedroom and get me some hay,
I open my window and spread it around,
For a moose always comes when there's hay on the ground!}

\verse{I went to the desert, a moose for to find
They only had camels; I near lost my mind,
For the thing that I learned about camels is this:
Where a moose always swallows, a camel just spits!}

\verse{Gorillas are all right for Saturday night,
And lions and tigers put up a good fight,
But nothin's as good when you slam that caboose
As the feeling you get when you're humpin' a moose.}

\verse{I've had many creatures on land and on sea,
I've even tried ostrich; they didn't like me.
A shark is all right, but they're hard to get loose
So I think that I'll stick with my beautiful moose.}

\verse{And when I arrive at the end of my years,
I'll have no regrets and I'll shed me no tears,
I'll stand on my porch with a glass of vermouth,
Playin' hide the salami with my favourite mooth!}

\verse{I've died, gone to Heaven; my soul flees away,
I'll show up at those gates with a bale of hay,
St. Pete's bound to inquire as to my wicked grin,
So I'll wind up in Hell fuckin' mooses again.}